### 2025-02-12 BAI/exercises.tex
Updated lecture questions.

  \begin{solution}
    \begin{enumerate}
      \item Neuro-symbolic systems combine symbolic and connectionist AI by integrating symbolic reasoning with neural network processing. These systems use symbolic rules to guide neural network learning and decision-making.
      \item Symbolic rules can be extracted from neural networks by analyzing the learned weights and activations of the network to identify patterns and rules that explain the network's behavior.
      \item Different architectures for integrating symbolic and neural computing include neural-symbolic integration, where symbolic reasoning is combined with neural network processing, and neural-symbolic learning, where neural networks are used to learn symbolic rules from data.
      \item Images can be processed by a neural network using convolutional layers to extract features from the input data and fully connected layers to classify the features. The processing steps can be visualized by examining the activations and weights of the network at each layer.
      \item Hybrid systems and explainable AI are in the current focus of research because they provide a way to combine the strengths of symbolic and connectionist AI, improve the interpretability of AI systems, and enable more transparent and accountable decision-making.
    \end{enumerate}
  \end{solution}
\end{exercise}

>>>>

  \begin{solution}
    \begin{enumerate}
      \item Neuro-symbolic systems combine symbolic and connectionist AI by integrating symbolic reasoning with neural network processing. These systems use symbolic rules to guide neural network learning and decision-making.
      \item Symbolic rules can be extracted from neural networks by analyzing the learned weights and activations of the network to identify patterns and rules that explain the network's behavior.
      \item Sequential architecture: neural network processing followed by (higher-level) symbolic reasoning. Embedding knowledge in neural networks: symbolic knowledge is encoded in the network's weights. Recurrent neural-symbolic models: continuous feedback between neural and symbolic processing. Knowledge-based NNs: symbolic rules are directly incorporated into the network architecture.
      \item Process images with CNN, visualize by analyzing the activations of the network, e.g., by using gradient-based methods to highlight important features.
      \item It is becoming increasingly important to explain AI systems and make their decisions transparent and interpretable. Hybrid systems combine the strengths of symbolic and neural computing to provide more robust and explainable AI solutions.
    \end{enumerate}
  \end{solution}
\end{exercise}
